---
title: "BROWNIAN_MOTION_2"
author: "NGUYEN NGOC PHUNG"
date: "12/14/2020"
output:
  word_document: default
  html_document: default
---
### GENERATE A PATH OF BROWNIAN MOTION

#### Let's |Π| = {t0, t1, ..., tn} be a partition of [0, t]
#### Let's n=100,000, t=2, we have the following Brownian motion @-@

```{r}
# we use the fact that B(t)=X1+X2+...+Xn (where each Xi follow N(0,t/n))
Path_BM<- function(n,t)
{
  Path<-c(0,cumsum(rnorm(n,0,t/n)))
  return(Path)
}

Path<-Path_BM(100000,1)
step<-seq(0,1,length=100001)
plot(step,Path, type="l")
```

### GENERATE A FUCNTION TO GET A PATH OF VARIARIATION OF ORDER-N OVER TIME INTERVAL [0,T]

```{r}
#first, we create a function to see value of n-order variation over time interval [0,t]
order<-function(Path,order)
{
  n<-length(Path)-1
  x<-numeric(n)
  for(i in 1:n)
  {
    ab<-abs(Path[i+1]-Path[i])
    x[i]<-ab^order
  }
  #now we cumsum the absolute value of |f(ti+1) − f(ti)|^n and assign that value to Path_nth_order
  Path_nth_order<-cumsum(x)
  return(Path_nth_order)
}
```

### FIRST-ORDER VARIATION

#### F VT (f) = lim sigma|f(ti+1) − f(ti)|

```{r}

#we have the first-order variation of Path is
n<-100000
order(Path,1)[n]

#now, I want to see the changes of first order variation over the time interval [0,1]
P<-order(Path,1)
step<-seq(1/n,1,length=n)
plot(step,P,type="l",col="red")

#OBSERVATION: the first_order variation increase over time interval [0,1], if we use linear regression to find out the slope equal @-@
lm(step~P)
```

### SECOND-ORDER VARIATION

#### F VT (f) = lim sigma|f(ti+1) − f(ti)|^2

```{r}

#we have the second-order variation of Path is
n<-100000
order(Path,2)[n]

#now, I want to see the changes of second order variation over the time interval [0,1]
P<-order(Path,2)
step<-seq(1/n,1,length=n)
plot(step,P,type="l",col="red")

#OBSERVATION: the second_order variation increase over time interval [0,1], if we use linear regression to find out the slope equal @-@ 
#Note: the slope would be much smaller than the slope of 1_st order
lm(step~P)
```

### THIRD-ORDER VARIATION

#### F VT (f) = lim sigma|f(ti+1) − f(ti)|^3

```{r}

#we have the third-order variation of Path is
n<-100000
order(Path,3)[n]

#now, I want to see the changes of third order variation over the time interval [0,1]
P<-order(Path,3)
step<-seq(1/n,1,length=n)
plot(step,P,type="l",col="red")

#OBSERVATION: the third_order variation increase over time interval [0,1], if we use linear regression to find out the slope equal @-@ 
#Note: the slope would be smaller than the slope of 1_st and 2nd order
lm(step~P)
```


### FORTH-ORDER VARIATION

#### F VT (f) = lim sigma|f(ti+1) − f(ti)|^4

```{r}

#we have the forth-order variation of Path is
n<-100000
order(Path,4)[n]

#now, I want to see the changes of forth order variation over the time interval [0,1]
P<-order(Path,4)
step<-seq(1/n,1,length=n)
plot(step,P,type="l",col="red")

#OBSERVATION: the third_order variation increase over time interval [0,1], if we use linear regression to find out the slope equal @-@ 
#Note: the slope would be smaller than the slope of 1_st,2nd and 3rd order
lm(step~P)
```

### FIFTH-ORDER VARIATION

#### F VT (f) = lim sigma|f(ti+1) − f(ti)|^5

```{r}

#we have the fifth-order variation of Path is
n<-100000
order(Path,5)[n]

#now, I want to see the changes of fifth order variation over the time interval [0,1]
P<-order(Path,5)
step<-seq(1/n,1,length=n)
plot(step,P,type="l",col="red")

#OBSERVATION: the third_order variation increase over time interval [0,1], if we use linear regression to find out the slope equal @-@ 
#Note: the slope would be smaller than the slope of above order
lm(step~P)
```


### BROWNIAN MOTION WITH DRIFT

#### CREATE A FUNCTION TO GENERATE PATH OF BROWNIAN MOTION WITH DRIFT

```{r}
Path_BM_drift<-function(n,t,miu,sigma)
{
  Path_Bt<-Path_BM(n,t)
  Path_Xt<-numeric(n+1)
  step<-seq(0,t,length=(n+1))
  for(i in 1:(n+1))
  {
    Path_Xt[i]<-(miu*step[i])+(sigma*Path_Bt[i])
  }
  return(Path_Xt)
}

P<-Path_BM_drift(10000,1,0.06,2)
step<-seq(0,1,length=10001)
plot(step,P, type="l")
```

#### DRIFT TERM: we gonna figure out the effect of drift term miu to the trend and movement of Brownnian motion

```{r}
# first, we create an arbitrary vector of 50 different drift terms from normal(0,4) @-@
miu<-sort(rnorm(50,0,0.5),decreasing = F)
# see the graph of vector miu
plot(miu,type="l")

n<-10001
sigma<-2

#second, we create a table of 50 different paths of Brownian motion with drift with constant sigma=2
Table_miu<-matrix(0,50,n)
for(i in 1:50)
{
  m<-miu[i]
  path_i<-Path_BM_drift(n,1,m,sigma)
  for(j in 1:n)
  {
    Table_miu[i,j]<-path_i[j]
  }
}

#finally, we plot all 50 paths in a graph @-@
library(ggplot2)
 y<-as.vector(t(Table_miu))
 df <- data.frame(x=rep(seq(0,1,1/10000),50), y=y, 
                  variable=rep(paste0("", 1:50), each=10001))
 ggplot(data = df, aes(x=x, y=y)) + geom_line(aes(colour=variable))
 
 # CONCLUSION: value of miu determine the trend of our Brownian motion.
 # For miu>0, the higher mu, the BM is more likely to increase faster
 # For miu<0, the lower mu , the BM is more likely to decrease faster
```


#### DIFFUSION TERM: we gonna figure out the effect of diffusion term sigma to the trend and movement of Brownnian motion

```{r}
# first, we create a vector of 50 diffusion terms by Chi-square (df=4) @-@
sigma<-sort(rchisq(50,4),decreasing = F)
#I want to see the graph of sigma
plot(sigma,type="l")

n<-10001
miu<-0.005

#second,we create a table of 50 different paths of Brownian motion with drift with constant miu=1
Table_sigma<-matrix(0,50,n)
for(i in 1:50)
{
  s<-sigma[i]
  path_i<-Path_BM_drift(n,1,miu,s)
  for(j in 1:n)
  {
    Table_sigma[i,j]<-path_i[j]
  }
}

#finally, we plot all 50 paths in a graph @-@
library(ggplot2)
 y<-as.vector(t(Table_sigma))
 df <- data.frame(x=rep(seq(0,1,1/10000),50), y=y, 
                  variable=rep(paste0("", 1:50), each=10001))
 ggplot(data = df, aes(x=x, y=y)) + geom_line(aes(colour=variable))
 


 # CONCLUSION: the diffusion parameter sigma determine the spread of BM. In orther words, the higher sigma is likely to lead to larger spread of BM.
 
```

### GEOMETRIC BROWNIAN MOTION FOR STOCK PRICE

#### COCA COLA COMPANY

```{r}
data_KO<-read.csv('C:/Users/Win 10/Documents/KO.csv')
head(data_KO)
#since we take only close price (Sk)
stock_price<-data_KO$Close
n<-length(stock_price)

#now, we generate a vector of returns by using formula rk=ln(Sk/Sk-1)
log_return<-numeric(n-1)
for(i in 1:(n-1))
{
  log_return[i]<-log(stock_price[i+1]/stock_price[i])
}

#histogram of return of Coca cola company look like this *-*
hist(log_return, col="blue")

#we have mean(log_return)=r-sigma^2/2 and sd(log_return)=sigma
#where r is interest rate and sigma= daily volatility of return *-*
sigma<-sd(log_return)
r<-mean(log_return)+(sigma^2)/2

#Hence, we have:
r
sigma

```


#### FACEBOOK CORPORATION

```{r}
data_FB<-read.csv('C:/Users/Win 10/Documents/FB.csv')
head(data_FB)
#since we take only close price (Sk)
stock_price<-data_FB$Close
n<-length(stock_price)

#now, we generate a vector of returns by using formula rk=ln(Sk/Sk-1)
log_return<-numeric(n-1)
for(i in 1:(n-1))
{
  log_return[i]<-log(stock_price[i+1]/stock_price[i])
}

#histogram of return of Coca cola company look like this *-*
hist(log_return, col="blue")

#we have mean(log_return)=r-sigma^2/2 and sd(log_return)=sigma
#where r is interest rate and sigma= daily volatility of return *-*
sigma<-sd(log_return)
r<-mean(log_return)+(sigma^2)/2

#Hence, we have:
r
sigma

```
