---
title: "BROWNIAN MOTION_SUNDAY"
author: "NGUYEN NGOC PHUNG"
date: "11/28/2020"
output:
  pdf_document: default
  word_document: default
  html_document: default
---
### BROWNIAN MOTION PATH (IN 4 WAYS)
#### Create the standard Brownian motion paths knowing the time and the lenth of paths
```{r}
#way number 1
#we use the fact that B(ti)= B(ti-1)+Xi (where Xi folow N(0,t/n))
Path_way1 <-function(n,t)
{
  Path<-numeric(n+1)
  Path[1]<-0
  for(i in 2:(n+1))
  {
    normal<-rnorm(1,0,t/n)
    Path[i]<-Path[i-1]+normal
  }
  return(Path)
}

Path1<-Path_way1(10000,2)
step<-seq(0,2,length=10001)
plot(step,Path1, type="l")

# way number 2
#we use the fact that Xi=sqrt(t/n)*Zi, we generate a vector of Zi, then B(ti)= sqrt(t/n)*(Z1+Z2+...+Zn)

Path_way2 <-function(n,t)
{
  Path<-c(0,cumsum(rnorm(n)))
  return(Path)
}

Path2<-Path_way2(10000,2)
step<-seq(0,2,length=10001)
plot(step,Path2, type="l")

#way number 3
# we use the fact that B(t)=X1+X2+...+Xn (where each Xi follow N(0,t/n))
Path_way3<- function(n,t)
{
  Path<-c(0,cumsum(rnorm(n,0,t/n)))
  return(Path)
}

Path3<-Path_way3(10000,2)
step<-seq(0,2,length=10001)
plot(step,Path3, type="l")


#way number 4
#we construct Brownian motion through scaled symetric random walk with large n
Random_Walk_Path<-function(M0,n,p,X)
{
  #M0 is the starting point @-@
  #n is number of walks 
  #p=P(H), so P(T)=(1-p)
  #X is positive value of Xn
  value<-c(X,-X)
  Path<-numeric(n+1)
  Path[1]<-M0
  for(i in 2:(n+1))
  {
    Xn<-sample(value,1,prob=c(p,1-p))
    Path[i]<-Path[i-1] + Xn
  }
  return(Path)
}

Scaled_Random_Walk_Path<-function(M0,n,t,p,X)
{
  #we will generate a RW in interval [0,t] with the scale n
  N<-n*t
  Wt<-numeric(N)
  Path<-Random_Walk_Path(M0,N,p,X)
  for(i in 1:N)
  {
    Wt[i]<-(1/sqrt(n))*Path[i]
  }
  return(Wt)
}

Path4<-Scaled_Random_Walk_Path(0,10000,2,1/2,1)
step<-seq(1/10000,2,length=20000)
plot(step,Path4, type="l")



# EXTRA: I want to see 20 paths of Brownian motion @-@
 
 Table_Path<-matrix(0,20,10001)
 for(i in 1:20)
 {
   P<-Path_way2(10000,1)
   for(j in 1:10001)
   {
     Table_Path[i,j]<-P[j]
   }
 }
 
 library(ggplot2)
 y<-as.vector(t(Table_Path[1:20,]))
 df <- data.frame(x=rep(seq(0,10,10/10000),20), y=y, 
                  variable=rep(paste0("", 1:20), each=10001))
 ggplot(data = df, aes(x=x, y=y)) + geom_line(aes(colour=variable))
```

### INVARIANCE PRINCIPLE

#### The Donsker's invariance principle stated that when we start with "any" i.i.d sequence of RVs X1,X2,...,Xn with E[Xi]=0 and Var[Xi]=1
#### Let Mn=X1+...+Xn
#### S(nt)/sqrt(n) will converge to Bt as n-> inf

#### we create 2 sequence of Xi and follow the above steps to generate Brownian motion
#### Sequence 1: P(Xi=-2)=P(Xi=2)=1/8, P(Xi=0) =3/4
#### Sequence 2: P(Xi=-1)=1/3, P(Xi=0)=1/2, P(Xi=2)=1/6
```{r}
# we let n=10,000 and t=1
# first, we generate a path for sequence 1
n<-10000
X1<-numeric(n)
for(i in 1:n)
{
  X1[i]<-sample(c(-2,0,2),1,prob=c(1/8,3/4,1/8))
}
Path1<-c(0,1/sqrt(n)*cumsum(X1))
step<-seq(0,1,length=(n+1))
plot(step,Path1, type="l")

# second, we generate a path for sequence 2
X2<-numeric(n)
for(i in 1:n)
{
  X2[i]<-sample(c(-1,0,2),1,prob=c(1/3,1/2,1/6))
}
Path2<-c(0,1/sqrt(n)*cumsum(X2))
step<-seq(0,1,length=(n+1))
plot(step,Path2, type="l")

# so we can clearly see that the Donsker's invariance principle hold for any sequence Xi with E[Xi]=0, Var[Xi]=1 @-@
```

### TRANSFORMATION OF BROWNIAN MOTION

#### REFLECTION, TRANSLATION, RESCALING, INVERSION (Bt)t>0 is Standard Brownian motion

#### REFLECTION: (-Bt)t>0 is standard Brownian motion
```{r}
#we will show the reflection principle by drawing 2 paths, the original and the its reflection in order to know what is the differences @-@
n<-10000
t<-10
Path_o<-Path_way1(n,t)
Path_r<- -Path_o
step<-seq(0,10, length=n+1)

library(ggplot2)
df <- data.frame(step,Path_o,Path_r)
ggplot(df, aes(step)) +                    
  geom_line(aes(y=Path_o), colour="red") +  
  geom_line(aes(y=Path_r), colour="green")


# now we plot 20 paths of (-Bt)t>0 @-@
Table_Path_r<- -Table_Path
library(ggplot2)
 y<-as.vector(t(Table_Path_r[1:20,]))
 df <- data.frame(x=rep(seq(0,10,10/10000),20), y=y, 
                  variable=rep(paste0("", 1:20), each=10001))
 ggplot(data = df, aes(x=x, y=y)) + geom_line(aes(colour=variable))

```

#### TRANSLATION: (B(t+s)-Bs)t>0 for all s>=0

```{r}
# we will show the reflection principle by drawing 2 paths, the original and the its translation in order to know what is the differences @-@
# we take s=3, which means we take 3001st value @-@
n<-10000
t<-10
Path_o<-Path_way2(n,t)
Bs<-Path_o[3001]
Path_t<- numeric(7001)
for (i in 1:7001)
{
  Path_t[i]<-Path_o[3000+i]-Bs
}
step1<-seq(0,10,10/n)
step2<-seq(0,7,10/n)
x<-c(3,3)
y<-c(Bs-0.05,-Bs+0.05)
df1<-data.frame(step1,Path_o)
df2<-data.frame(step2,Path_t)
df3<-data.frame(x,y)

p = ggplot() + 
  geom_line(data = df1, aes(x =step1 , y = Path_o), color = "blue") +
  geom_line(data = df2, aes(x = step2, y =Path_t), color = "red") +
  geom_line(data = df3, aes(x = x, y = y), color = "black") 

print(p)

# now we plot 20 paths of (B(t+s)-Bs)t>0 @-@
Table_Path_t<- matrix(0,20,7001)
for(i in 1:20)
{
  Bs<-Table_Path[i,3001]
for (j in 1:7001)
{
  Table_Path_t[i,j]<-Table_Path[i,3000+j]-Bs
}
}
library(ggplot2)
 y<-as.vector(t(Table_Path_t[1:20,]))
 df <- data.frame(x=rep(seq(0,7,10/10000),20), y=y, 
                  variable=rep(paste0("", 1:20), each=7001))
 ggplot(data = df, aes(x=x, y=y)) + geom_line(aes(colour=variable))

```

#### RESCALING: 1/sqrt(a)*B(at) (t>0) for all a>0 is standard Brownian motion

```{r}
n<-20000
t<-2
a<-2
Path_o<-Path_way2(n,t)
step1<-seq(0,2,2/20000)
step2<-seq(0,1,1/20000)
Path_re<-1/sqrt(a)*Path_o
df1<-data.frame(step1,Path_o)
df2<-data.frame(step2,Path_re)

p = ggplot() + 
  geom_line(data = df1, aes(x =step1 , y = Path_o), color = "blue") +
  geom_line(data = df2, aes(x = step2, y =Path_re), color = "red") 
 
print(p)

``` 

#### INVERSION: The process (Xt)t>0 defined by X0=0 and Xt=t*B(1/t)






