---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
load("brfss2013.RData")
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
#we need to load the package

```



* * *

## Part 1: Data
```{r}

#first, we want to view all the attributes of the data-frame
names(brfss2013)
#in order to see its dimension and data types
str(brfss2013)
```

* * *

## Part 2: Research questions

**Research quesion 1:**
QUESTION 1: SUMMARIZING NUMBER OF SLEEP (zzz)

```{r}
str(brfss2013$sleptim1)
Q1<-brfss2013 %>%
  filter(!is.na(sleptim1)) 
Q1 %>% summarise(mean = mean(sleptim1),sd=sd(sleptim1),count=n())
#I plot it in bar graph
ggplot(data = Q1, aes(x = factor(sleptim1))) +
    geom_bar()

```

**Research quesion 2:**
QUESTION 2: AVERAGE ALCOHOL DRINK OF THOSE HAVE SUFFERED FROM DEPRESSION
```{r}
brfss2013 %>% filter(!is.na(avedrnk2)) %>% summarise(mean = mean(avedrnk2),sd=sd(avedrnk2),count=n())
#Structure of 2 attributes
str(brfss2013$addepev2)
str(brfss2013$avedrnk2)
#get rid of NA value and people have not suffered from depression then assign to Q2
Q2<-brfss2013 %>%
  filter(as.numeric(addepev2)==1,!is.na(addepev2),!is.na(avedrnk2)) 
Q2 %>% summarise(mean = mean(avedrnk2),sd=sd(avedrnk2),count=n())

```

**Research quesion 3:**
QUESTION 3: SEGMENTED BAR PLOT BETWEEN AVERAGE ALCOHOL DRINK AND (NOT) HAVING SUFFERED FROM DEPRESSION

```{r}
Q3<-brfss2013 %>%
  filter(!is.na(addepev2),!is.na(avedrnk2)) 
ggplot(data = Q3, aes(x = addepev2 , fill = factor(avedrnk2))) +
  geom_bar()
``` 


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

QUESTION 1: CALCULATE PEOPLE'S UNHEALTHY DAYS BASED ON THEIR PHYSICAL AND EMOTIONAL HEALTH, THEN FIND THEIR RELATIONSHIP THROUGH SEGMENTED BAR-PLOT

```{r}
#First, I want to see the structure of number of day physical and mental health is not good @-@
str(brfss2013$physhlth)
str(brfss2013$menthlth)
#Then, I will exclude all NA row and assign new data.frame to QUES1
QUES1<-brfss2013 %>% filter(!is.na(physhlth),!is.na(menthlth))
# I want to see the summary of these 2 attributes @-@
QUES1 %>% summarise(meanphy=mean(physhlth),sdphy=sd(physhlth),minphy=min(physhlth),maxphy=max(physhlth),count=n())
QUES1 %>% summarise(meanphy=mean(menthlth),sdphy=sd(menthlth),minphy=min(menthlth),maxphy=max(menthlth),count=n())
#Then I plot it in segmented bar plot
ggplot(data = QUES1, aes(x = physhlth, fill = factor(menthlth))) +geom_bar()
#So we can clearly see that, a large number of unhealthy day is zero, and as number of physically unhealthy day is 0, remarkably large number of mentally unhealthy day is 0 @-@
```



**Research quesion 2:**

QUESTION 2: WE CLAIM THAT PEOPLE WITH HIGH EDUCATION LEVEL GONNA HAVE HIGH INCOME LEVEL, I WILL CHECK THIS BY USING ATTIBUTE EDUCA AND INCOME2

```{r}
#First, I want to see the structure of educational and income level
str(brfss2013$educa)
str(brfss2013$income2)
#Then, I will exclude all NA row and assign new data.frame to QUES2
QUES2<-brfss2013 %>% filter(!is.na(educa),!is.na(income2))
#Then I plot it in segmented bar plot @-@
ggplot(data = QUES2, aes(x = as.numeric(educa), fill = income2)) +geom_bar()
#So we can clearly see the strong possitive relationship between educational level and income level, which infer that people having high educational level tend to gain more income *-*
```



**Research quesion 3:**

QUESTION 3: CHECK THE RELATIONSHIP BETWEEN PEOPLE SMOKING FREQUENCY AND HAVING PULMONARY DISEASE 

```{r}
#First, I want to see the structure of having pulmonary disease and frequency of smoking
str(brfss2013$chccopd1)
str(brfss2013$smokday2)
#Then, I will exclude all NA row and assign new data.frame to QUES3
QUES3<-brfss2013 %>% filter(!is.na(chccopd1),!is.na(smokday2))
#Then I plot it in segmented bar plot @-@
ggplot(data = QUES3, aes(x = chccopd1, fill = smokday2)) +geom_bar()
#surprisingly, large amount of people reported smok every day do not suffer from pulmonary disease
```


## THE END 

