---
title: "MARKOV CHAIN (SUNDAY ANSWER)"
author: "NGUYEN NGOC PHUNG"
date: "10/24/2020"
output: html_document
---

### EXAMPLE 1:
#### Alice is taking a probability class and in each week she can be either up-to-date or she may have fallen behind. If she is up-to-date in a given week, the probability that she will be up-to-date (or behind) in the next week is 0.8 (or 0.2, respectively). If she is behind in the given week, the probability that she will be up-to-date (or behind) in the next week is 0.6 (or 0.4, respectively). We assume that these probabilities do not depend on whether she was up-to-date or behind in previous weeks, so the problem has the typical Markov chain character (the future depends on the past only through the present).
#### QUESTION 1: create the state space S and transition matrix P, draw transition diagram (*)

```{r}
#the state space is 
S<-c(1,2)
S
#the transition matrix is
P<-matrix(c(0.8,0.6,0.2,0.4),2,2)
P
```
#### QUESTION 2: create a path of length 10 given X0=1

```{r}
path_10<-numeric(11)
path_10[1]<-1
for(i in 2:11)
{
  if(path_10[i-1]==1) {path_10[i]<-sample(S,1,prob=c(0.8,0.2))}
  if(path_10[i-1]==2) {path_10[i]<-sample(S,1,prob=c(0.6,0.4))}
}
path_10

```
#### QUESTION 3: create 10 paths of length 10 given P(X0=1)=0.6, P(X0=2)=0.4

```{r}
X0<-sample(S,1,prob=c(0.6,0.4))
path_10<-matrix(0,10,11)
for (i in 1:10)
{
  path_10[i,1]<-X0
  for(j in 2:11)
  {
    if(path_10[i,j-1]==1) {path_10[i,j]<-sample(S,1,prob=c(0.8,0.2))}
  if(path_10[i,j-1]==2) {path_10[i,j]<-sample(S,1,prob=c(0.6,0.4))}
  }
}
path_10
```

#### QUESTION 4: create a function to generate 1 path of any length n for any transition matrix. Then create a path of length 100 in this example

```{r}
PATH<-function(n,P,S,init_proba)
{
  number_S<-length(S)
  X0<-sample(S,1,prob=init_proba)
  Path<-numeric(n+1)
  Path[1]<-X0
  for(i in 2:(n+1))
  { 
    for(k in 1:number_S)
    {
      if(Path[i-1]==S[k]) {Path[i]<-sample(S,1,prob=P[k,])}
    }
  }
  return(Path)
}

PATH(100,P,S,c(0.6,0.4))
```

#### QUESTION 5: create 100 paths of length 10 given P(X0=1)=0.6, P(X0=2)=0.4
```{r}
Path_100<-matrix(0,100,11)
for(i in 1:100)
{
  Path_row<-PATH(10,P,S,c(0.6,0.4))
  for(j in 1:11)
  {
    Path_100[i,j]<-Path_row[j]
  }
}

#the first 10 rows is
Path_100[1:10,]

```

#### QUESTION 6: find 2-step and 3-step transition matrix P2, P3 (*)
```{r}
P2<-P%*%P
P2
P3<-(P%*%P)%*%P
P3
P3<-P2%*%P
P3
```

#### QUESTION 7: find 100-step transition matrix P100
```{r}
matrixpower <- function(mat,k) {
  if (k == 0) return (diag(dim(mat)[1])) 
  if (k == 1) return(mat)
  if (k > 1) return( mat %*% matrixpower(mat, k-1))
}
matrixpower(P,5)
matrixpower(P,10)
P100<-matrixpower(P,100)
P100
```







