---
title: "POISSON PROCESS (2)"
author: "NGUYEN NGOC PHUNG"
date: "10/18/2020"
output:
  word_document: default
  html_document: default
---
## SIMULATION POISSON (SUBMIT)

####  Simulate and plot a path of Poisson process with intensity lambda  = 2 on [0,3] by 2 approaches

### EXPONENTIAL DISTRIBUTION OF INTER-ARRIVAL TIME            
```{r}
#first, we need to make a function for generating Poisson process using inter-arrival time @-@
Poisson_processX<-function(lamda,t)
{
  X<-numeric(1)
  X[1]<-rexp(1,lamda)
  while(sum(X)<t) 
  {
    n<-length(X)
    length(X)<-n+1
    X[n+1]<-rexp(1,lamda)
  }
  return(X)
}
#So the sequence of inter-arrival time X with lamda=2 in [0,3] is
X<-Poisson_processX(2,3)
X

 #then our poisson process will look  like the following @-@
n<-length(X)
N<-numeric(n) ; time<-numeric(n)
for(i in 1:n)
{
  N[i]<-i
  time[i]<-sum(X[1:i])
}
library(ggplot2)
ggplot()+
  geom_step(aes(x=time, y=N))+
  scale_x_continuous(breaks=time)+
  theme_bw()

```

### CONDITIONAL DISTRIBUTION OF ARRIVAL TIME

```{r}
#second, we will make a function for generating Poisson process using conditional arrival time @-@
Poisson_process_S<-function(lamda,t)
{
  n<-rpois(1,lamda)
  uni<-numeric(n)
  for(i in 1:n)
  {
    uni[i]<-runif(1,0,t)
  }
  S<-sort(uni,decreasing = FALSE)
  return(S)
}
#So the sequence of arrival time S with lamda=2 in [0,3] is
S<-Poisson_process_S(2,3)
S
 #then our poisson process will look  like the following @-@
N<-1:length(S)
time<-S
library(ggplot2)
ggplot()+
  geom_step(aes(x=time, y=N))+
  scale_x_continuous(breaks=time)+
  theme_bw()
```

## SIMULATION POISSON (OPTIONAL)

#### Q1: Simulate a path of Poisson process with rate λ = 2 on interval time [0, 10] by simulating inter-arrival time
```{r}
#Sequence of inter-arrival time X with lamda=2 in [0,10] is
X<-Poisson_processX(2,10)
X

 #then our poisson process will look  like the following @-@
n<-length(X)
N<-numeric(n) ; time<-numeric(n)
for(i in 1:n)
{
  N[i]<-i
  time[i]<-sum(X[1:i])
}
library(ggplot2)
ggplot()+
  geom_step(aes(x=time, y=N))+
  scale_x_continuous(breaks=time)+
  theme_bw()

```

#### Q2: Simulate a path of Poisson process with rate λ = 2 on interval time [0, 10] by simulating number of event Nt first and then arrival times (using conditional distribution of arrival times)
```{r}
#Sequence of arrival time S with lamda=2 in [0,10] is
S<-Poisson_process_S(2,10)
S
 #then our poisson process will look  like the following @-@
N<-1:length(S)
time<-S
library(ggplot2)
ggplot()+
  geom_step(aes(x=time, y=N))+
  scale_x_continuous(breaks=time)+
  theme_bw()
```

#### Q3: Simulate a path of insurance surplus on [0, 10] with

#### (Nt)t is a poisson process with rate λ = 2

#### Claim size Wk ,→ Exp(1)

```{r}

#CRAMER_LUNDBERG
#now we will create a function for Cramer_Lundberg problem @-@
Cramer_Lundberg<-function(lamdaN,lamdaW,x0,c,t)
{
  #first, we find the path of inter-arrival times X in [0,t]
  X<-Poisson_processX(lamdaN,t) 
  #so there are n number of arrivals in [0,t]
  n<-length(X)
  #second, we create an insurance surplus path for drawing U_draw (which mean this path contains all the point in our drawing) @-@
  #Beside, We also create an insurance surplus path U @-@
  U<-numeric(n+1)
  U_draw<-numeric(2*n+1)
  
  U[1]<-x0
  U_draw[1]<-x0
  for (i in 1:n)
  {
    U_draw[2*i]<-x0+c*X[i]
    W<-rexp(1,lamdaW)
    U_draw[(2*i)+1]<-U_draw[2*i]-W
    U[i+1]<-U_draw[(2*i)+1]
    x0<-U_draw[(2*i)+1]
  }
  #then we return a list of 2 paths, path of X and path of U
  mylist<-list(X,U,U_draw)
  return(mylist)
}

Path<-Cramer_Lundberg(2,1,10,1,10)
#Since our Path is in list form of X and U, we need to unlist
X<-unlist(Path[1])
U_draw<-unlist(Path[3])

X
U_draw

#DRAW INSURANCE SURPLUS *-*
n<-length(X)
time<-numeric((2*n)+1)
time[1]<-0
for(i in 1:n)
{
  S<-sum(X[1:i])
  time[(2*i)]<-S
  time[(2*i)+1]<-S
}

library(ggplot2)
ggplot()+
  geom_point(aes(x=time,y=U_draw))+
  geom_line(aes(x=time,y=U_draw))+
  ylab("U(t)")+
  theme_bw()


```

#### QUESTION 4: Estimate ruin probability of the previous problem on finite horizon time [0, 10] with c = 1, x = 10, (Nt)t is a poisson process with rate λ = 2, claim size Wk ,→ Exp(1)

```{r}
#Now we create a function to calculate ruin probability @-@
RUIN_PROBABILITY<-function(lamdaN,lamdaW,x0,c,t)
{
  #we simulate 100000 times Cramer_Lundberg function and count number of path being ruined
  #we count number of path having negative U(t)
  count<-0
  for(i in 1:100000)
  {
    Path<-Cramer_Lundberg(lamdaN,lamdaW,x0,c,t)
    U<-unlist(Path[2])
    n<-length(U)
    negative<-0
    for(j in 1:n)
    {
      if(U[j]<0) {negative<-1; break}
    }
    count<-count+negative
  }
  Ruin_proba<-count/100000
  return(Ruin_proba)
}

#So the ruin probability in [0,10] with c = 1, x = 10, (Nt)t is a poisson process with rate λ = 2, claim size Wk ,→ Exp(1) is *-*
RUIN_PROBABILITY(2,1,10,1,10)
```

#### QUESTION 5: Which value of c should be to guarantee that the ruin probability over horizon time [0, 10] is less or equal to 10−3 .Use set up as the previous as (except value of c)

```{r}
#Since, the larger the c, the smaller ruin probability
#we can solve this problem by some numerical method @-@
#starting from c=1, we increase c by 1 each times until ruin probability reach 10^(-3)
c<-1
while(RUIN_PROBABILITY(2,1,10,c,10)>0.001)
{
  c<-c+1
}
c
```

#### PRACTICE QUESTION: Consider the compound Poisson process modeling aggregate health claims; frequency N is a Poisson process with rate λ = 20 per day and severity W is an Exponential random variable with mean θ = 500. Simulate 10000 scenarios for the aggregate claims S10 during the first 10 days.
#### 1. Estimate E(R10) and V ar(R10) from simulated sample.
#### 2. Plot histogram for simulated sample of R10. What can you say about the distribution of R10.
#### 3. Propose an approximation or estimation for P(R10 > 120, 000).

```{r}
#First, we create a function to find 1 scenarios for R(t)
Cramer_Lundberg_R<-function(lamdaN,lamdaW,t)
{
  n<-rpois(1,lamdaN*t)
  sum<-0
  for (i in 1:n)
  {
    W<-rexp(1,lamdaW)
    sum<-sum+W
  }
  return(sum)
}
#Then, we simulate 10000 times scenarios for R10
R10<-numeric(10000)
for (i in 1:10000)
{
  R10[i]<-Cramer_Lundberg_R(20,1/500,10)
}
#the first 10 values of S10 is
R10[1:10]

# E[R10] and Var[R10] is as follwing @-@
mean(R10)
var(R10)

#Histogram of R10 @-@
hist(R10,
main="Aggregated Claim R10",
xlab="value of R10",
col="darkmagenta"
)

#Find P(R10>120000)
count<-0
for(i in 1:10000)
{
  if(R10[i]>120000) {count<-count+1}
}
#so P(R10>120000) is
count/10000
```


