---
title: "Q-Q PLOT (BONUS)"
author: "NGUYEN NGOC PHUNG"
date: "1/4/2021"
output:
  html_document: default
  word_document: default
---

### COCA COLA COMPANY

```{r}
data_KO<-read.csv('C:/Users/Win 10/Documents/KO.csv')
data_KO[1:20,]

#since we take only close price (Sk)
stock_price<-data_KO$Close
n<-length(stock_price)

#now, we generate a vector of returns by using formula rk=ln(Sk/Sk-1)
log_return<-numeric(n-1)
for(i in 1:(n-1))
{
  log_return[i]<-log(stock_price[i+1]/stock_price[i])
}

#histogram of return of Coca cola company look like this *-*
hist(log_return, col="blue")

# now we have Q-Q plot look as the following:

qqnorm(log_return, pch = 1, frame = FALSE)
qqline(log_return, col = "steelblue", lwd = 2)

```

#### FACEBOOK CORPORATION

```{r}
data_FB<-read.csv('C:/Users/Win 10/Documents/FB.csv')
data_FB[1:20,]

#since we take only close price (Sk)
stock_price<-data_FB$Close
n<-length(stock_price)

#now, we generate a vector of returns by using formula rk=ln(Sk/Sk-1)
log_return<-numeric(n-1)
for(i in 1:(n-1))
{
  log_return[i]<-log(stock_price[i+1]/stock_price[i])
}

#histogram of return of Coca cola company look like this *-*
hist(log_return, col="blue")

# now we have Q-Q plot look as the following:

qqnorm(log_return, pch = 1, frame = FALSE)
qqline(log_return, col = "steelblue", lwd = 2)
