---
title: "RANDOM WALK_SUNDAY"
author: "NGUYEN NGOC PHUNG"
date: "11/21/2020"
output: html_document
---

## SYMMETRIC RANDOM WALK

### Simulate Path, Draw Random walk, Find PMF of Mn, Find PMF of increment (Mn-Mm) (n>m)

#### QUESTION 1: Build a function for simulating a path of symmetric random walk @-@
```{r}
Random_Walk_Path<-function(M0,n,p,X)
{
  #M0 is the starting point @-@
  #n is number of walks 
  #p=P(H), so P(T)=(1-p)
  #X is positive value of Xn
  value<-c(X,-X)
  Path<-numeric(n+1)
  Path[1]<-M0
  for(i in 2:(n+1))
  {
    Xn<-sample(value,1,prob=c(p,1-p))
    Path[i]<-Path[i-1] + Xn
  }
  return(Path)
}
```

#### QUESTION 2: Use the function to generate a path of 100 walks for P(H)=1/2, Xn=1 or Xn=-1 @-@
```{r}
Random_Walk_Path(0,100,0.5,1)
```

#### QUESTION 3: Simulate 10,000 paths with same info in Question 2
```{r}
Table_paths<-matrix(0,10000,100)
for (i in 1:10000)
{
  Path<-Random_Walk_Path(0,100,0.5,1)
  for(j in 1:100)
  {
    Table_paths[i,j]<-Path[j+1]
  }
}
 #so the first 10 line with first 50 walks is like the following
Table_paths[1:10,1:50]

```

#### QUESTION 4a: Find expected value of M50 and M70 by 10000 paths generated
```{r}
M50<-numeric(10000)
for (i in 1:10000)
{
  M50[i]<-Table_paths[i,50]
}
#so the expected value is 
sum(M50)/10000

# There is other way shorter *-*
sum(Table_paths[,50])/10000

#By the same way, the expected value of M70 is
sum(Table_paths[,70])/10000
```

#### QUESTION 4b: Find expected value of Mn (n=1,2,...,100) by 10000 paths generated
```{r}
Expected_value<-numeric(100)
for(i in 1:100)
{
 Expected_value[i]<- sum(Table_paths[,i])/10000
}
#Since this is symmetric random walk, hence {Mn} is a martingale, it is reasonable that E[Mn] should be merely equal for all n *-*
```

#### QUESTION 5: Draw the histogram of M50, M70 @-@
```{r}
hist(M50, main="Value of M50")
#or we can do by other way
hist(Table_paths[,70],main="Value of M70")
```

#### QUESTION 6: Find the expectation and variance of (M75-M25)
```{r}
# QUESTION 6: Find the expectation and variance of (M75-M25)
M25_M75<-numeric(10000)
for(i in 1:10000)
{
  M25_M75[i]<-Table_paths[i,75]-Table_paths[i,25]
}
#so the E(M75-M25) and Var(M75-M25) is
sum(M25_M75)/10000
var(M25_M75)
#they must be near to 0 and 50 respectively *-*
```

#### QUESTION 7: Build a function to graphically draw the random walk
```{r}
Draw_Random_Walk <- function(M0,n,p,X)
{
  path<-Random_Walk_Path(M0,n,p,X)
  Mn<-numeric(n+1)
  Mn[1]<-0
  step<-numeric(n+1)
  step[1]<-0
  for(i in 2:(n+1))
  {
    Mn[i]<-path[i-1]
    step[i]<-(i-1)
  }
  library(ggplot2)
ggplot()+
  geom_point(aes(x=step,y=Mn))+
  geom_line(aes(x=step,y=Mn))+
  ylab("Mn")+
  theme_bw()
}

#for example, we draw the previous exercise @-@
Draw_Random_Walk(0,100,0.5,1)

```

#### QUESTION 8 (hard): Draw the first 50 paths 
```{r}
y<-as.vector(t(Table_paths[1:50,]))
df <- data.frame(x=rep(1:100,50), y=y, 
         variable=rep(paste0(1:50), each=100))
ggplot(data = df, aes(x=x, y=y)) + geom_line(aes(colour=variable))
```

#### QUESTION 9: Create a vector of expected value of Xi (E[X1],...,E[X100]) and a vector for Variance of Xi (Var[X1],...,Var[X100])
```{r}
#create 2 all-zero vectors for Expected value and Variance
E<-numeric(100)
V<-numeric(100)
for(i in 1:100)
{
  E[i]<-mean(Table_paths[,i])
  V[i]<-var(Table_paths[,i])
}
#So we have the following table for expectation and variance for our paths, it would be reasonable if Expected values is merely 0 and variance increase as t increase
rbind(E,V)

plot(E,type="l")
plot(V,type="l")

```

### First passage time 

#### QUESTION 1: Build a function to find first passage time of a path
```{r}
Tm<-function(Path,m)
{
  n<-length(Path)
  Set<-numeric(n)
  for(i in 1:n)
  {
    if(Path[i]==m) {Set[i]<-i}
    else {Set[i]<-NA}
  }
  if(all(is.na(Set)==TRUE)) {Tm<-NA}
  else {Tm<-min(Set, na.rm=TRUE)}
  return(Tm)
}
```

#### QUESTION 2: For 10000 paths simulated above, find 10000 values of T1

```{r}
T1<-numeric(10000)
for (i in 1:10000)
{
  T1[i]<-Tm(Table_paths[i,],1)
}

#so the first 10 values of T1 is
T1[1:10]
```

#### QUESTION 3: Histogram of T1

```{r}
hist(T1, main="First passage time T1", col="darkmagenta")
```

#### QUESTION 4: For 10000 paths simulated above, find 10000 values of T3 and histogram of T3

```{r}
T3<-numeric(10000)
for (i in 1:10000)
{
  T3[i]<-Tm(Table_paths[i,],3)
}

#so the first 10 values of T3 and histogram of T3 is
T3[1:10]
hist(T3, main="First passage time T3", col="darkmagenta")

```

### Reflection principle

#### QUESTION 1: Create a Table of Paths containing all the paths having T3<=5,then choose randomly 30 paths in that table and draw it to see the reflection principle
```{r}
# first, we have that T3 is vector containing values of T3 in 10000 paths
row_number<-c()
for(i in 1:10000)
{
  if((is.na(T3[i])==FALSE)&&(T3[i]<=5)) {row_number<-c(row_number,i)}
}
#the first 50 values of row_number is @-@
row_number[1:50]

#then, we create a Table for Paths with T3<=5
n<-length(row_number)
Table_Reflect_T3<-matrix(0,n,100)
for(i in 1:n)
{
  row<-row_number[i]
  Path<-Table_paths[row,]
  for(j in 1:100)
  {
    Table_Reflect_T3[i,j]<-Path[j]
  }
}


y<-as.vector(t(Table_Reflect_T3[1:30,]))
df <- data.frame(x=rep(1:100,30), y=y, 
         variable=rep(paste0(1:30), each=100))
ggplot(data = df, aes(x=x, y=y)) + geom_line(aes(colour=variable))

```

## SCALED SYMMETRIC RANDOM WALK

### Simulate Path, Draw Path, Compare as n increase

#### QUESTION 1: Based on the function of random walk built above, build a function to simulate path for scaled random walk 

```{r}
Scaled_Random_Walk_Path<-function(M0,n,t,p,X)
{
  #we will generate a RW in interval [0,t] with the scale n
  N<-n*t
  Wt<-numeric(N)
  Path<-Random_Walk_Path(M0,N,p,X)
  for(i in 1:N)
  {
    Wt[i]<-(1/sqrt(n))*Path[i]
  }
  return(Wt)
}

```

#### QUESTION 2: Simulate a path of scaled symmetric random walk for t in [0,10] and n=10,100,1000,10000

```{r}
Path_10<-Scaled_Random_Walk_Path(0,10,10,0.5,1)
Path_10[1:10]
Path_100<-Scaled_Random_Walk_Path(0,100,10,0.5,1)
Path_100[1:10]
Path_1000<-Scaled_Random_Walk_Path(0,1000,10,0.5,1)
Path_1000[1:10]
Path_10000<-Scaled_Random_Walk_Path(0,10000,10,0.5,1)
Path_10000[1:10]

```

####QUESTION 3: Build a function to graphically draw the scaled symmetric random walk
```{r}
Draw_Scaled_Random_Walk <- function(M0,n,t,p,X)
{
  path<-Scaled_Random_Walk_Path(M0,n,t,p,X)
  Wt<-numeric((n*t)+1)
  Wt[1]<-0
  step<-numeric((n*t)+1)
  step[1]<-0
  for(i in 2:((n*t)+1))
  {
    Wt[i]<-path[i-1]
    step[i]<-(i-1)/n
  }
  library(ggplot2)
ggplot()+
  geom_line(aes(x=step,y=Wt))+
  ylab("Wt")+
  theme_bw()
}

#for example, we draw the previous exercise @-@
# for n=10
Draw_Scaled_Random_Walk(0,10,10,0.5,1)
# for n=100
Draw_Scaled_Random_Walk(0,100,10,0.5,1)
# for n=1000
Draw_Scaled_Random_Walk(0,1000,10,0.5,1)
# for n=10000
Draw_Scaled_Random_Walk(0,10000,10,0.5,1)
#for n=100000
Draw_Scaled_Random_Walk(0,100000,10,0.5,1)
```

#### QUESTION 4: Find the distribution of W(1.4),W(2.56),W(3.7),W(5.62),W(9.22),W(10) with n=1000 in[0,10]
```{r}
#first, we need to have a table to record 10000 paths of W(t)
Path_scale<-matrix(0,10000,10000)
for(i in 1:10000)
{
  Path<-Scaled_Random_Walk_Path(0,1000,10,0.5,1)
  for(j in 1:10000)
  {
    Path_scale[i,j]<-Path[j]
  }
}
# value of W(1.4) is at column 1400
W_1.4 <-Path_scale[,1400]
hist(W_1.4,main = "W(1.4)",col="blue")

#value of W(2.56) is at column 2560
W_2.56 <-Path_scale[,2560]
hist(W_2.56,main = "W(2.56)",col="blue")

#value of W(3.7) is at column 3700
W_3.7 <-Path_scale[,3700]
hist(W_3.7,main = "W(3.7)",col="blue")

#value of W(5.62) is at column 5620
W_5.62 <-Path_scale[,5620]
hist(W_5.62,main = "W(5.62)",col="blue")

#value of W(9.22) is at column 9220
W_9.22 <-Path_scale[,9220]
hist(W_9.22,main = "W(9.22)",col="blue")

#value of W(10) is at column 10000
W_10 <-Path_scale[,10000]
hist(W_10,main = "W(10)",col="blue")

```






