---
title: "SIMULATION (EXERCISE 8)"
author: "NGUYEN NGOC PHUNG"
date: "9/25/2020"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

## ASIAN OPTION

### QUESTION 1
 Find cdf of V3 and then simulate 10000 random number for V3. Use them to estimate E(V3) and error of estimation at confidence level 95%. Compare to the exact value
 
*We have S0=4, u=2=1/d, p=q=0.5, K=4
*Let Y3=S0+S1+S2+S3
*we have V3=((Y3/4)-4)+

*By listing all the possible outcomes of V3, we have the following:

V3(HHH)=11; V3(HHT)=5; V3(HTH)=2

V3(THH)=V3(HTT)=0.5

V3(TTH)=V3(THT)=V3(TTT)=0

*Since each possible outcomes has the same probability is 1/8

*The PMF of V3 is:

 P(V3=0)  =3/8; P(V3=0.5)=2/8;  P(V3=2)  =1/8
 
 P(V3=5)  =1/8; P(V3=11) =1/8
 
*So Expected number of V3 is:
 E(V3)=2.375
 
 The CDF of V3 is:
 F(V3)= 0  (V3<0) ; F(V3)= 3/8(0<=V3<0.5)
 
 F(V3)= 5/8(0.5<=V3<2) ;  F(V3)= 6/8(2<=V3<5)
 
 F(V3)= 7/8(5<=V3<11) ; F(V3)= 1  (V3>=11)
 
 *Assume that X is a discrete random variable such that P(X=xi)=pi.
 The algorithm proceeds as follows:
 
 1. Generate U∼Unif(0,1) 
 2. Determine the index k such that ∑k−1j=1pj≤U<∑kj=1pj, and return X=xk.

 *We need to create a function called transform_method first 
 
```{r}
transform_method <- function( vector,value ) {
  U  <- runif(1)
  if(U <= vector[1]){
    return(value[1])
  }
  for(state in 2:length(vector)) {
    if(sum(vector[1:(state-1)]) < U && U <= sum(vector[1:state]) ) {
      return(value[state])
    }
  }
}
```

*Then we generate 10000 values of V3 by inverse transform method and find E[V3]  (^-^)

```{r}
n<-10000
vector<- c(3/8,2/8,1/8,1/8,1/8)
value <- c(0,0.5,2,5,11)
samples     <- numeric(n)
for(i in seq_len(n) ) 
  {
  samples[i] <- transform_method(vector,value)
}
#So the first 100 values of 10000 generating values for V3 look like the following:
samples[1:100]
#expected number of V3 generated is:
expect<-sum(samples)/n
expect
#Since the real expected value is 2.375, so the relative error is:
error<-abs(2.375-expect)/2.375
error
#Histogram for V3:
hist(samples,prob=TRUE,col="blue", main='ANSIAN OPTION Q1')
lines(density(samples),col="red")
```

### QUESTION 2
Simulate a path (S1, S2, S3). Use it to generate random number of Y3. Repeat 10000 times to simulate 10000 random number of Y3. Use them to estimate E(V3) and error of estimation at confidence level 95%.
Compare to the exact value

1. Generating 10000 sequence S of stock price from S0 to S3
2. Find Y3 of each Sequence S
3. Find V3 of each sequence S
4. Find E(V3) then compare it to exact value

*First, I make a function to generate a sequence S (^_^)


```{r}
S<-function(s0,u,p,n)
{
  #s0 is initial price,u is up factor, p is p(H), n is periods
  price<-numeric(n+1)
  price[1]<-s0
  for (i in 1:n)
  {
    Berno<-rbinom(1,1,p)
    if(Berno==1) {price[i+1]<-price[i]*u} else {price[i+1]<-price[i]/u}
  }
  return(price)
}
```

*Now, we generate 10000 sequence of stock price, for each sequence, we find Y3 and E3> Then find E(V3) and error (HIHI)

```{r}
data<-matrix(0,10000,6)
dimnames(data)<-list(1:10000,c("S0","S1","S2","S3","Y3","E3"))
for(i in 1:10000)
{
  price<-S(4,2,0.5,3)
  for(j in 1:4)
  {
    data[i,j]<-price[j]
  }
  data[i,5]<-sum(price)
  data[i,6]<-max((data[i,5]/4)-4,0)
}
#So the first 10 rows of data look like following:
data[1:10,]
#Histogram for V3:
hist(data[,6],prob=TRUE,col="blue", main='ANSIAN OPTION Q2')
lines(density(data[,6]),col="red")
#expectation of V3
expect<-sum(data[,6])/10000
expect
#Since the real expected value is 2.375, so the relative error is:
error<-abs(2.375-expect)/2.375
error
#error of expectation in 95% confidence interval is
2*sd(data[,6])/(sqrt(10000))
```

## FLOATING LOOK BACK OPTION

### QUESTION 1
*We have S0=4, u=2=1/d, p=q=0.5
v3= max(Sn)-S3 (n in {0,1,2,3})

*Since each possible outcomes has the same probability is 1/8
 The PMF of V3 is:
 P(V3=0)  =3/8 ; P(V3=2)  =2/8
 
 P(V3=3.5)=1/8 ; P(V3=6)  =1/8 ; P(V3=8)  =1/8
 
 So Expected number of V3 is:
 E(V3)=2.6875
 
 The CDF of V3 is:
 F(V3)= 0  (V3<0) ; F(V3)= 3/8(0<=V3<2)
 F(V3)= 5/8(2<=V3<3.5) ; F(V3)= 6/8(3.5<=V3<6)
 F(V3)= 7/8(6<=V3<8) ; F(V3)= 1  (V3>=8)

*Similarly,we generate 10000 values of V3 by inverse transform method and find E[V3]  (^-^)

```{r}
n<-10000
vector<- c(3/8,2/8,1/8,1/8,1/8)
value <- c(0,2,3.5,6,8)
samples_float   <- numeric(n)
for(i in seq_len(n) ) 
  {
  samples_float[i] <- transform_method(vector,value)
}
#So the first 100 values of the 10000 generating values for V3 is:
samples_float[1:100]
#expected number of V3 generated is:
expect<-sum(samples_float)/n
expect
#Since the real expected value is 2.375, so the relative error is:
error<-abs(2.6875-expect)/2.375
error
#Histogram for V3:
hist(samples,prob=TRUE,col="blue", main='FLOATING LOOK BACK OPTION Q1')
lines(density(samples),col="red")
```

### QUESTION 2

1. Generating 10000 sequence S of stock price from S0 to S3
2. Find V3 of each sequence S
3. Find E(V3) then compare it to exact value

```{r}
data_float<-matrix(0,10000,5)
dimnames(data_float)<-list(1:10000,c("S0","S1","S2","S3","V3"))
for(i in 1:10000)
{
  price<-S(4,2,0.5,3)
  for(j in 1:4)
  {
    data_float[i,j]<-price[j]
  }
  data_float[i,5]<-max(price)-data_float[i,4]
}
#So the first 10 rows for floating back option is
data_float[1:10,]
#Histogram for V3:
hist(data_float[,5],prob=TRUE,col="blue", main='FLOATING BACK OPTION Q2')
lines(density(data_float[,5]),col="red")
#expectation of V3
expect<-sum(data_float[,5])/10000
expect
#Since the real expected value is 2.375, so the relative error is:
error<-abs(2.6875-expect)/2.375
error
#error of expectation in 95% confidence interval is
2*sd(data_float[,5])/(sqrt(10000))
```

## LOG RETURN

### QUESTION 1
 Simulate a path (W1, W2)
 
*Let S0, S1, S2... be stock price at period 0, 1, 2, 3... 
   S0=1
   
*The log-return of the period k is
Wk = ln (Sk/Sk−1)

*The cummulative log-return at period k is
Bk=ln (Sk/S0)


*We will do the following steps
1. Simulate 10000 (W1,W2) where W1 and W2 are i.i.d N(1,4)

2.Check whether W1 and W2 are N(1,4)

```{r}
#create a matrix W for (W1,W2)
W<-matrix(0,10000,2)
dimnames(W)<-list(1:10000,c("W1","W2"))
for (i in 1:10000)
{
  W[i,1]<-rnorm(1,1,2)
  W[i,2]<-rnorm(1,1,2)
}
#So the first 10 values of W is
W[1:10,]
#we can clearly see that W1 and W2 are N(1,4)
hist(W[,1],prob=TRUE,col="blue",main="Distribution of W1")
lines(density(W[,1]),col="red")
hist(W[,2],prob=TRUE,col="blue",main="Distribution of W2")
lines(density(W[,2]),col="red")
```

### QUESTION 2
Use (W1, W2) to generate (B1, B2)

*We will do the following steps

1. Simulate 10000 (B1,B2) where B1=W1 and B2=W1+W2 

2.Check whether B1 is N(1,4) and B2 is N(2,8)

```{r}
#create a matrix B for (B1,B2)
B<-matrix(0,10000,2)
dimnames(B)<-list(1:10000,c("B1","B2"))
for (i in 1:10000)
{
  B[i,1]<-W[i,1]
  B[i,2]<-sum(W[i,])
}
#So the first 10 values of B is
B[1:10,]
#we can clearly see that B1 is N(1,4) and B2 is N(2,8)
hist(B[,1],prob=TRUE,col="blue",main="Distribution of B1")
lines(density(B[,1]),col="red")
hist(B[,2],prob=TRUE,col="blue",main="Distribution of B2")
lines(density(B[,2]),col="red")
```
 

### QUESTION 3
 Use (B1, B2) to generate (S1, S2)

*So now we have B1 and B2, we want to find S1,S2 (S0=1)

*We have B1=ln(S1/S0)=ln(S1)
         B2=ln(S2/S0)=ln(S2)
         
*Hence, inversely we have:
 S1=exp(B1)
 S2=exp(B2)

*We will do the following steps

1. Simulate 10000 (S1,S2) where S1=exp(B1) and S2=exp(B2)

2.Check whether S1 and S2 are log-normal distribution

```{r}
#We create matrix S for (s1,S2)
S<-matrix(0,10000,2)
dimnames(S)<-list(1:10000,c("S1","S2"))
for (i in 1:10000)
{
  S[i,1]<-exp(B[i,1])
  S[i,2]<-exp(B[i,2])
}
#So the first 10 values of S is
S[1:10,]
#we can clearly see that S1 is Lognormal(1,4) and S2 is Lognormal(2,8)
S1_na<-numeric(10000)
 for (i in 1:10000)
 {
   if(S[i,1]<100) {S1_na[i]=S[i,1]} else {S1_na[i]=NA}
 }
 S1<-S1_na[complete.cases(S1_na)]
hist(S1,prob=TRUE,col="blue",main="Distribution of S1")
lines(density(S1),col="red")
  
hist(S[,2],prob=TRUE,col="blue",main="Distribution of S2")
lines(density(S[,2]),col="red")
```

### QUESTION 4
 Use S2 to generate V2. Repeat 1000 times.
Estimate E(V2) and error of estimation at confidence level 95%

*We find out that E(V2) is the integral from ln(3) to infinity of the function (exp(B2)-3)x(1/4sprt(pi))x(exp(-(B2-2)^2/16))

```{r}
#assign the function to exact_V2
exact_V2 <- function(x) {(1/(4*sqrt(pi)))*(exp(-1/2*((x-2)/sqrt(8))^2))*(exp(x)-3)}
#so the function look like this
curve(sapply(x,exact_V2), from=log(3), to=70,col="red")
#So we can see that value of B2 is mainly interval [log(3),25]
#So the exact expectation of V2 is @-@
integrate(exact_V2, lower = log(3), upper = 25)
integrate(exact_V2, lower = log(3), upper = 500)
#So the exact expected value of V2 is 401.2211 *-*
```

* Create a matrix called S2_to_V2
```{r}
S2_to_V2<-matrix(0,10000,2)
dimnames(S2_to_V2)<-list(1:10000,c("S2","V2"))
for(i in 1:10000)
{
  S2_to_V2[i,1]<-S[i,2]
  S2_to_V2[i,2]<-max(S2_to_V2[i,1]-3,0)
}
#So the first 10 values of generation from S2 to V2 is
S2_to_V2[1:10,]
#So the distribution of V2 look like the following
#Since the value of V2 is mainly in 0 to 500, so I only plot in this interval @-@
V2_na<-numeric(10000)
  for (i in 1:10000)
  {
    if(S2_to_V2[i,2]<500) {V2_na[i]=S2_to_V2[i,2]} else {V2_na[i]=NA}
  }
  V2<-V2_na[complete.cases(V2_na)]
  hist(V2,prob=TRUE,col="blue",main="Distribution of V2")
  lines(density(V2),col="red")
#expectation and error of V2 is
expect<-sum(S2_to_V2[,2])/10000
expect
#so the relative error of V2 is
abs(expect-401.2211)/401.2211
#error of expectation in 95% confidence interval is
2*sd(S2_to_V2[,2])/100000

```


### QUESTION 5 
Use (S1, S2) to generate Y2. Repeat 10000 times. 
Estimate E(V2A) and error of estimation at confidence level 95%

1. Simulate matrix containing S1,S2,Y2,V2A called G_Asian_option
2. Find E(V2A) and find the error

```{r}
#assign the function to exact_V2A
exact_V2A <- function(x) {(3/sqrt(40*pi))*(exp(x)-6)*(exp((-9/40)*(x-1)^2))}
#so the function look like this
curve(sapply(x,exact_V2A), from=log(6), to=70,col="red")
#So we can see that value of B2 is mainly interval [log(6),15]
#So the exact expectation of V2 is @-@
integrate(exact_V2A, lower = log(6), upper = 25)
integrate(exact_V2A, lower = log(6), upper = 500)
#So the exact value of V2A is 5.078954 *-*
```

```{r}
G_Asian_option<-matrix(0,10000,4)
dimnames(G_Asian_option)<-list(1:10000,c("S1","S2","Y2","V2A"))
for(i in 1:10000)
{
  G_Asian_option[i,1]<-S[i,1]
  G_Asian_option[i,2]<-S[i,2]
  G_Asian_option[i,3]<-(S[i,1]*S[i,2])^(1/3)
  G_Asian_option[i,4]<-max(G_Asian_option[i,3]-6,0)
}
#So the first 10 values of simulation of Geometric asian call option is
G_Asian_option[1:10,]
#So the distribution of V2A look like the following:
#Since value V2A is mainly on [0,30] so I plot only in this interval:
sum(G_Asian_option[,4]<30)
  V2A_na<-numeric(10000)
  for (i in 1:10000)
  {
    if(G_Asian_option[i,4]<30) {V2A_na[i]=G_Asian_option[i,4]} else {V2A_na[i]=NA}
  }
  V2A<-V2A_na[complete.cases(V2A_na)]
  hist(V2A,prob=TRUE,col="blue",main="Distribution of V2A")
  lines(density(V2A),col="red")
#expectation and error of V2A is
expect<-sum(G_Asian_option[,4])/10000
expect
#relative error is
abs(5.078954-expect)/5.078954
#error of expectation in 95% confidence interval is
2*sd(G_Asian_option[,4])/(sqrt(10000))
```
## THE END
















